Dewlap color variation in \textit{Anolis sagrei} is maintained among habitats within islands of the West Indies

### 2021-05-23 ms/sections/abstract.tex
addressed most immediate comments

Animal signals evolve in an ecological context. Locally adapting animal sexual signals can be especially important for initiating or reinforcing reproductive isolation during the early stages of speciation. Previous studies have demonstrated that dewlap color in \textit{Anolis} lizards can be highly variable between populations in relation to both biotic and abiotic adaptive drivers at relatively large geographical scales. Here, we investigated differentiation of dewlap coloration among habitat-types at a small spatial scale, within multiple islands of the West Indies, as this may give new insights into the local scale at which adaptation is possible. We explored variation in dewlap coloration in the most widespread species of anole, \textit{Anolis sagrei}, across three characteristic habitats spanning the Bahamas and the Cayman Islands. Using reflectance spectrometry as well as supervised machine learning, we found significant differences in spectral properties of the dewlap between habitats within small islands, sometimes over very short distances. Passive divergence in dewlap phenotype associated with isolation-by-distance did not explain our results. On the other hand, these habitat-specific dewlap differences varied in magnitude and direction across islands, and thus our primary test for adaptation -- parallel responses across islands -- was not supported. We suggest, however, that selection could be involved in several ways, including sexual selection. Our results shed new light on the scale at which signal color polymorphism can be maintained in the presence of gene flow, and the relative role of local adaptation and other processes in driving these patterns.

>>>>

Animal signals evolve in an ecological context. Locally adapting animal sexual signals can be especially important for initiating or reinforcing reproductive isolation during the early stages of speciation. Previous studies have demonstrated that dewlap color in \textit{Anolis} lizards can be highly variable between populations in relation to both biotic and abiotic adaptive drivers at relatively large geographical scales. Here, we investigated differentiation of dewlap coloration among habitat-types at a small spatial scale, within multiple islands of the West Indies, as this may give new insights into the local scale at which adaptation is possible. We explored variation in dewlap coloration in the most widespread species of anole, \textit{Anolis sagrei}, across three characteristic habitats spanning the Bahamas and the Cayman Islands. Using reflectance spectrometry paired with supervised machine learning, we found significant differences in spectral properties of the dewlap between habitats within small islands, sometimes over very short distances. Passive divergence in dewlap phenotype associated with isolation-by-distance did not explain our results. On the other hand, these habitat-specific dewlap differences varied in magnitude and direction across islands, and thus our primary test for adaptation -- parallel responses across islands -- was not supported. We suggest that selection could be involved in several ways, including sexual selection. Our results shed new light on the scale at which signal color polymorphism can be maintained in the presence of gene flow, and the relative role of local adaptation and other processes in driving these patterns.

### 2021-05-23 ms/sections/acknowledgments.tex
addressed most immediate comments

Collection permission was granted by the Bahamas Environment, Science and Technology Commission, the Bahamas National Trust, the Bahamas Ministry of Agriculture, and the Cayman Islands Department of the Environment. The authors thank Sofia Prado-Irwin, Pavitra Muralidhar, Nicholas Herrmann, Richard E. Glor, Alberto R. Puente-Rol\'{o}n, Kevin Aviles-Rodriguez, Kristin Winchell, Jason Fredette and Melissa Kemp for assistance in the field and Pratik Gupte, Max Lambert and James Stroud for helpful discussions. Funding for this work was provided by the Templeton Foundation (to JBL), NSF DEB~\#1927194 (to JBL and AJG), NSF DEB~\#1500761 (to AJG), NSF DBI~\#1609284 (to CMD), and a Harvard Museum of Comparative Zoology Putnam Expedition Grant (to RGR).

>>>>

Collection permission was granted by the Bahamas Environment, Science and Technology Commission, the Bahamas National Trust, the Bahamas Ministry of Agriculture, and the Cayman Islands Department of the Environment. The authors thank Sofia Prado-Irwin, Pavitra Muralidhar, Nicholas Herrmann, Richard E. Glor, Alberto R. Puente-Rol\'{o}n, Kevin Aviles-Rodriguez, Kristin Winchell, Jason Fredette, Quyhn Quach, Wendy Jesse, Inbar Maayan, Alexis Harrison and Melissa Kemp for assistance in the field and Pratik Gupte, Max Lambert and James Stroud for helpful discussions. Funding for this work was provided by the Templeton Foundation (to JBL), NSF DEB~\#1927194 (to JBL and AJG), NSF DEB~\#1500761 (to AJG), NSF DBI~\#1609284 (to CMD), and a Harvard Museum of Comparative Zoology Putnam Expedition Grant (to RGR).

### 2021-05-23 ms/sections/discussion2.tex
addressed most immediate comments

Detectable differences in dewlap color between habitat-populations are surprising, as habitats were often in close geographical proximity to each other (as close as a few hundred meters on Bimini and most of the time within ten kilometers). Indeed, given that (1) the populations were continuously distributed between the habitats, (2) different habitat-populations were not monophyletic with respect to mitochondrial haplotypes (van de Schoot, unpublished thesis), and (3) \textit{A. sagrei} have been shown to be a highly mobile species within these islands \citep{Kamath2018}, we would have expected more homogeneous distributions of color phenotypes within islands due to extensive gene flow, with fewer differences between populations, especially those in close proximity.\\

@@

Not only consistent patterns across islands would have been a good clue for a sensory-drive explanation, but in particular consistent differences between habitats that are most different in their local conditions regarding the ecological function of the dewlap, such as ambient light. For example, if ambient light is an important factor shaping dewlap coloration, we would expect mangrove and beach scrub lizards, both inhabiting areas with high light penetration, to harbor more similar dewlaps, and to differ significantly from lizards from the coppice habitat, where irradiance is low. Overall, the observed heterogeneity of divergence patterns across islands provides no support to a sensory-drive explanation.\\

@@

A number of alternative explanations remain. First, there could sexual selection for different dewlap colors in different locations. Indeed, although the sensory-drive hypothesis may include a sexual selection aspect, e.g. if the optimal male phenotype in a given habitat is a function of female perception, sexual preferences may also be arbitrary and independent of the habitat \citep{Andersson1994}, and so could differ across habitats and islands. Although one previous study has found no link between dewlap coloration and body size dimorphism in \textit{A. sagrei} (a proxy for the intensity of sexual selection) in an among-island comparison \citep{Baeckens2018}, within-island data are lacking to test the plausibility of this scenario.\\

>>>>

Detectable differences in dewlap color between habitat-populations are surprising, as habitats were often in close geographical proximity to each other (as close as a few hundred meters on Bimini and most of the time within ten kilometers). Indeed, given that (1) the populations were continuously distributed between the habitats, (2) different habitat-populations were not monophyletic with respect to mitochondrial haplotypes (\citealt{vandeSchoot2016} unpubl.), and (3) \textit{A. sagrei} have been shown to be a highly mobile species \citep{Kamath2018}, we would have expected more homogeneous distributions of color phenotypes within islands due to extensive gene flow, with fewer differences between populations, especially those in close proximity.\\

@@

Consistent patterns across islands would have been a good clue for a sensory-drive explanation, but in particular consistent differences between habitats that are most different in their local conditions regarding the ecological function of the dewlap, such as ambient light. For example, if ambient light is an important factor shaping dewlap coloration, we would expect mangrove and beach scrub lizards, both inhabiting areas with high light penetration, to harbor more similar dewlaps, and to differ significantly from lizards from the coppice habitat, where irradiance is low. Overall, the observed heterogeneity of divergence patterns across islands provides no support to a sensory-drive explanation.\\

@@

A number of alternative explanations remain. First, there could be sexual selection for different dewlap colors in different locations. Indeed, although the sensory-drive hypothesis may include a sexual selection aspect, e.g. if the optimal male phenotype in a given habitat is a function of female perception, sexual preferences may also be arbitrary and independent of the habitat \citep{Andersson1994}, and so could differ across habitats and islands. Although one previous study has found no link between dewlap coloration and body size dimorphism in \textit{A. sagrei} (a proxy for the intensity of sexual selection) in an among-island comparison \citep{Baeckens2018}, within-island data are lacking to test the plausibility of this scenario.\\

### 2021-05-23 ms/sections/introduction.tex
addressed most immediate comments

The staggering diversity of animal communication signals has long been of interest to evolutionary biologists. Animals use chemical, mechanical, electromagnetic, and visual signals to communicate in a wide variety of contexts, including, competition for mates, species recognition, aposematism, and cooperation \citep{Bradbury2011}. A primary evolutionary factor shaping communication signals is the sensory system and behavior of their recipients (the sensory drive hypothesis; \citealt{Endler1988,Endler1992,Endler1998}). Over the past decades, scientists have established that signals evolve in an ecological context and are dependent on environmental conditions \citep{Endler1992,Endler1993,Endler1993a}. Just as different habitats may favor different combinations of eco-morphological traits to maximize performance and fitness \citep{Arnold1983}, they may also shape different forms of a signal, so as to maximize its transmission and detection (e.g. \citealt{Seehausen1997}), or reduce its detection by unintended recipients such as predators \citep{Endler1984,Endler1990,Endler1991,Halfwerk2014}. This selective pressure may drive the local adaptation of communication signals.\\

@@

One potential barrier to the maintenance of localized signal divergence is the homogenizing effect of gene flow. Population genetics theory suggests that gene flow may counteract local adaptation between localities and prevent divergence altogether, especially at small spatial scales, because of the inflow of maladapted alleles or because of the breaking of linkage between coevolving loci \citep{Felsenstein1976, Garcia-Ramos1997, Dieckmann1999, Lenormand2002, Hendry2007}. This genetic homogenization has been confirmed empirically in systems such as stick-insects \citep{Nosil2004} and sticklebacks \citep{Hendry2007a}. Yet, examples of microgeographic adaptation, i.e. adaptation at smaller scales than the range of dispersal, exist, highlighting the potential of some organisms to respond to selection in the face of gene flow (see \citealt{Richardson2014} and references therein). Examples include small scale adaptation in fragmented areas in Australian fruit flies \citep{Willi2012}, or local adaptation to predation pressure in North American salamanders \citep{Richardson2013}. Therefore, despite evidence that local adaptation may be particularly difficult at small spatial scales where gene flow tends to cause adjoining populations to remain genetically homogeneous, the potential adaptive response of species traits, in particular communication signals, to localized differences in habitats remains relatively unknown \citep{Richardson2014}.\\

@@

Lizards of the neotropical genus \textit{Anolis} are an excellent group for studying the eco-evolutionary dynamics of local adaptation and natural selection \citep{Losos2009}. A particularly conspicuous trait of anoles is their dewlap; an extensible flap of skin that is typically sexually dimorphic and used as a communication signal in courtship \citep{Sigmund1983, Driessens2014, Driessens2015} and territorial displays \citep{Losos1985, Macedonia1994, Macedonia2013} as well as in predator deterrence \citep{Leal1995, Leal1997, Leal1997b}. Dewlap characteristics vary widely among the approximately $400$ species of the genus \citep{Nicholson2007}. Interspecific variation in dewlap coloration is implicated in species recognition \citep{Rand1970b, Williams1969, Williams1977, Losos1985, Macedonia1994, Fleishman2000, Macedonia2013}, and this function could have had a role in initiating and/or reinforcing reproductive isolation during speciation \citep{Lambert2013, Geneva2015, Ng2017}.\\

Within species, studies have shown a link between variation in dewlap coloration and differences in habitats or climatic conditions \citep{Macedonia2001, Leal2002, Thorpe2002a, Thorpe2002b, Leal2004, Vanhooydonck2009, Ng2012, Ng2013, Ng2016, Vanhooydonck2009, Driessens2017}. Some studies suggest that those differences may be adaptive, and that dewlaps may have evolved to maximize detectability given local light conditions \citep{Fleishman2001, Leal2002, Leal2004}. Although this claim is further supported by recent findings that dewlap colors are perceived differently under different levels of shading \citep{Fleishman2020}, other studies found conflicting patterns of between-habitat variation that did not support the sensory drive hypothesis \citep{Fleishman2009, Ng2012, Macedonia2014a}.\\

Previous studies investigating variation in anole dewlaps compared populations at relatively large geographical scales, e.g. between islands \citep{Vanhooydonck2009, Driessens2017} or within large islands such as Puerto Rico \citep{Leal2004} or Hispaniola \citep{Ng2012, Ng2016}. These large scales and marine barriers should reduce gene flow \citep{Ng2011, Lambert2013, Richardson2014, Ng2017}. That said, examples do exist of divergence in dewlap coloration at smaller scales or between populations with high degrees of gene flow \citep{Thorpe2002a, Thorpe2002b, Stapley2011, Ng2016}.\\

The species \textit{Anolis sagrei} is widespread across islands of the West Indies \citep{Reynolds2020}. It has been the subject of numerous studies concerning local adaptation \citep{Losos1994, Losos1997a, Losos2001, Kolbe2012}, biological invasion \citep{Kolbe2008}, sexual selection \citep{Tokarz2002, Tokarz2005, Tokarz2006, Driessens2014, Steffen2014, Driessens2015} and many other topics. Between-island variation in the mainly orange-red color of its dewlap was shown to be better explained by climatic variables \citep{Driessens2017} than by proxies for biotic factors such as sexual selection or predation pressure \citep{Vanhooydonck2009, Baeckens2018}. How intra-island differences in habitat may contribute to the diversity of dewlap coloration, however, remains unexplored, and may reveal new insights into the scale of local differentiation despite gene flow.\\

@@

Here, we analyzed the color characteristics of \textit{A. sagrei} dewlaps within nine islands in the Bahamas and Cayman Islands. These island systems presently, if not historically, comprise relatively small islands, with no major geographic barriers within islands limiting dispersal for this promiscuous species \citep{Kamath2018}. These islands all share three characteristic native West Indian habitat-types -- beach scrub bush, closed-canopy primary coppice forest, and mangrove forest -- that are often spatially intermingled. These habitats contrast in environmental parameters including vegetation community, light irradiance, humidity and temperature \citep{Howard1950, Schoener1968}. The Cayman Islands and the Bahamas have been colonized independently by \textit{A. sagrei} from Cuba (\citealt{Reynolds2020}, van de Schoot et al. unpubl.), such that these archipelagos constitute an ideal suite of natural replicates to explore within-island dewlap diversity across multiple islands.\\

>>>>

The staggering diversity of animal communication signals has long been of interest to evolutionary biologists. Animals use chemical, mechanical, electromagnetic, and visual signals to communicate in a wide variety of contexts, including, competition for mates, species recognition, aposematism, and cooperation \citep{Bradbury2011}. A primary evolutionary factor shaping communication signals is the sensory system and behavior of recipients (the sensory drive hypothesis; \citealt{Endler1988,Endler1992,Endler1998}). Over the past decades, scientists have established that signals evolve in an ecological context and are dependent on environmental conditions \citep{Endler1992,Endler1993,Endler1993a}. Just as different habitats may favor different combinations of eco-morphological traits to maximize performance and fitness \citep{Arnold1983}, they may also shape different forms of a signal, so as to maximize its transmission and detection (e.g. \citealt{Seehausen1997}), or reduce its detection by unintended recipients such as predators \citep{Endler1984,Endler1990,Endler1991,Halfwerk2014}. This selective pressure may drive the local adaptation of communication signals.\\

@@

One potential barrier to the maintenance of localized signal divergence is the homogenizing effect of gene flow. Population genetics theory suggests that gene flow may counteract local adaptation between localities and prevent divergence altogether, especially at small spatial scales, because of the inflow of maladapted alleles or because of the breaking of linkage between coevolving loci \citep{Felsenstein1976, Garcia-Ramos1997, Dieckmann1999, Lenormand2002, Hendry2007}. This genetic homogenization has been confirmed empirically in systems such as stick-insects \citep{Nosil2004} and stickleback \citep{Hendry2007a}. Yet, examples of microgeographic adaptation, i.e. adaptation at smaller scales than the range of dispersal, exist, highlighting the potential of some organisms to respond to selection in the face of gene flow (see \citealt{Richardson2014} and references therein). Examples include small scale adaptation in fragmented areas in Australian fruit flies \citep{Willi2012}, or local adaptation to predation pressure in North American salamanders \citep{Richardson2013}. Therefore, despite evidence that local adaptation may be particularly difficult at small spatial scales where gene flow tends to cause adjoining populations to remain genetically homogeneous, the potential adaptive response of species traits, in particular communication signals, to localized differences in habitats remains relatively unknown \citep{Richardson2014}.\\

@@

Lizards of the neotropical genus \textit{Anolis} are an excellent group for studying the eco-evolutionary dynamics of local adaptation and natural selection \citep{Losos2009}. A particularly conspicuous trait of anoles is their dewlap; an extensible flap of skin that is typically sexually dimorphic and used as a communication signal in courtship \citep{Sigmund1983, Driessens2014, Driessens2015} and territorial displays \citep{Losos1985, Macedonia1994, Macedonia2013} as well as in predator deterrence \citep{Leal1995, Leal1997, Leal1997a}. Dewlap characteristics vary widely among the approximately $400$ species of the genus \citep{Nicholson2007}. Interspecific variation in dewlap coloration is implicated in species recognition \citep{Rand1970, Williams1969, Williams1977, Losos1985, Macedonia1994, Fleishman2000, Macedonia2013}, and this function could have had a role in initiating and/or reinforcing reproductive isolation during speciation \citep{Lambert2013, Geneva2015, Ng2017}.\\

Within species, studies have shown a link between variation in dewlap coloration and differences in habitats or climatic conditions \citep{Macedonia2001, Leal2002, Thorpe2002, Thorpe2002a, Leal2004, Vanhooydonck2009, Ng2012, Ng2013, Ng2016, Vanhooydonck2009, Driessens2017}. Some studies suggest that those differences may be adaptive, and that dewlaps may have evolved to maximize detectability given local light conditions \citep{Fleishman2001, Leal2002, Leal2004}. Although this claim is further supported by recent findings that dewlap colors are perceived differently under different levels of shading \citep{Fleishman2020}, other studies found conflicting patterns of between-habitat variation that did not support the sensory drive hypothesis \citep{Fleishman2009, Ng2012, Macedonia2014}.\\

Previous studies investigating variation in anole dewlaps compared populations at relatively large geographical scales, e.g. between islands \citep{Vanhooydonck2009, Driessens2017} or within large islands such as Puerto Rico \citep{Leal2004} or Hispaniola \citep{Ng2012, Ng2016}. These large scales and marine barriers should reduce gene flow \citep{Ng2011, Lambert2013, Richardson2014, Ng2017}. That said, examples do exist of divergence in dewlap coloration at smaller scales or between populations with high degrees of gene flow \citep{Thorpe2002, Thorpe2002a, Stapley2011, Ng2016}.\\

The species \textit{Anolis sagrei} is widespread across islands of the West Indies \citep{Reynolds2020}. It has been the subject of numerous studies concerning local adaptation \citep{Losos1994, Losos1997a, Losos2001, Kolbe2012}, biological invasion \citep{Kolbe2008}, sexual selection \citep{Tokarz2002, Tokarz2005, Tokarz2006, Driessens2014, Steffen2014, Driessens2015} among many other topics. Between-island variation in the mainly orange-red color of its dewlap was shown to be better explained by climatic variables \citep{Driessens2017} than by proxies for biotic factors such as sexual selection or predation pressure \citep{Vanhooydonck2009, Baeckens2018}. How intra-island differences in habitat may contribute to the diversity of dewlap coloration, however, remains unexplored, and may reveal new insights into the scale of local differentiation despite gene flow.\\

@@

Here, we analyzed the color characteristics of \textit{A. sagrei} dewlaps within nine islands in the Bahamas and Cayman Islands. These island systems presently, if not historically, comprise relatively small islands, with no major geographic barriers within islands limiting dispersal for this promiscuous species \citep{Kamath2018}. These islands all share three characteristic native West Indian small-island habitat-types -- beach scrub bush, closed-canopy primary coppice forest, and mangrove forest -- that are often spatially intermingled. These habitats contrast in environmental parameters including vegetation community, light irradiance, humidity, and temperature \citep{Howard1950, Schoener1968}. The Cayman Islands and the Bahamas have been colonized independently by \textit{A. sagrei} from Cuba (\citealt{vandeSchoot2016} unpublished thesis; \citealt{Reynolds2020}), such that these archipelagos constitute an ideal suite of natural replicates to explore within-island dewlap diversity across multiple islands.\\

### 2021-05-23 ms/sections/methods2.tex
addressed most immediate comments

We performed a machine learning classification analysis on the first four principal components within each island separately, using random forests \citep{Breiman2001}. Random forests are a versatile, intuitive and powerful algorithm commonly used in machine learning, using decision trees to predict the labels of particular observations, based on their multivariate coordinates, i.e. variables, passed through a series of successive decision nodes, each examining a given variable of any given observation \citep{James2013}. The prediction for each observation is an aggregate over a large number of decision trees, each being trained on a subset of observations sampled with replacement from the dataset, and each allowed to examine only a subset of the variables. This allows the random forest to overcome the individual errors of all trees in the predictions it makes.\\

To detect differences in dewlap coloration between habitats, we measured the success of random forests in reassigning individual lizards to their correct habitat of origin, based solely on their principal component scores. In machine learning, this so-called cross-validation procedure is typically done in two steps \citep{James2013}. First, a random forest is trained in recognizing features of dewlap coloration most associated with the different habitats, by being presented multiple observations, making predictions about them and updating its own decision rules based on whether the prediction deviates from the truth. Then, once trained, the patterns that the random forest has learned to recognize are tested by presenting new, previously unseen observations to the random forest, and measuring the proportion of correct predictions. This proportion, or success score, can then be statistically assessed against random guessing using a binomial test.\\

The cross-validation procedure requires that the data be split into a training set and a testing set. To remove any bias due to the set that is being sampled for training, it is common practice to use k-fold cross-validation \citep{James2013}, where the data is split into $k$ random bins and $k$ independent machines are trained, each taking one of the bins as a testing set and the rest for training, and where classification success is measured by summing all correct classifications from the $k$ machines.\\

@@

We used the machine learning fitting functions in the R package rminer \citep{Cortez2020}, which call random forest routines from the randomForest package (\citealt{Liaw2002}, implementation from the original random forest algorithm, \citealp{Breiman2001}). For each random forest, we optimized the number of trees in the forest and the number of variables examined by each tree using the grid hyperparameter search procedure implemented in rminer, to choose between two numbers of trees (500 or 1,000) and four numbers of principal components examined per tree (1 to 4), using rminer's ordered holdout validation method with $2/3$ of the data used for training.\\

@@

In this study, we were interested in the minimum spatial scale at which significant differences between habitats could be detected within islands. We performed multiple pairwise nonparametric Wilcoxon-Mann-Whitney tests \citep{Hollander2013} to compare dewlap coloration between sites with different habitat-types, for each pair of habitats and each variable where significant differences were detected with our analyses of variances. The P-values were adjusted using a Benjamini-Hochberg correction for multiple testing \citep{Benjamini1995}.

>>>>

We performed a machine learning classification analysis on the first four principal components within each island separately, using random forests \citep{Breiman2001}. Random forests are a versatile, intuitive, and powerful algorithm commonly used in machine learning, using decision trees to predict the labels of particular observations based on their multivariate coordinates. These coordinates, or variables, are passed through a series of successive decision nodes, each examining a given variable of any given observation \citep{James2013}. The prediction for each observation is an aggregate over a large number of decision trees, each tree being trained on a subset of observations sampled with replacement from the dataset, and each tree being allowed to examine only a subset of the variables. This allows the random forest to overcome the individual errors of all trees in the predictions it makes.\\

To detect differences in dewlap coloration between habitats, we measured the success of random forests in reassigning individual lizards to their correct habitat of origin, based solely on their principal component scores. In machine learning, this so-called cross-validation procedure is typically done in two steps \citep{James2013}. First, a random forest is trained in recognizing features of dewlap coloration most associated with the different habitats, by being presented with multiple observations, making predictions about them, and updating its own decision rules based on whether the prediction deviates from the truth. Then, once trained, the patterns that the random forest has learned to recognize are tested by presenting new, previously unseen observations to the random forest, and measuring the proportion of correct predictions. This proportion, or success score, can then be statistically assessed against random guessing using a binomial test.\\

The cross-validation procedure requires that the data be split into a training set and a testing set. To remove any bias due to the set that is being sampled for training, it is common practice to use k-fold cross-validation \citep{James2013}, where the data are split into $k$ random bins and $k$ independent machines are trained, each taking one of the bins as a testing set and the rest for training, and where classification success is measured by summing all correct classifications from the $k$ machines.\\

@@

We used the machine learning fitting functions in the R package rminer \citep{Cortez2020}, which calls random forest routines from the randomForest package (\citealt{Liaw2002}, implementation from the original random forest algorithm, \citealp{Breiman2001}). For each random forest, we optimized the number of trees in the forest and the number of variables examined by each tree using the grid hyperparameter search procedure implemented in rminer, to choose between two numbers of trees (500 or 1,000) and four numbers of principal components examined per tree (1 to 4), using rminer's ordered holdout validation method with $2/3$ of the data used for training.\\

@@

In this study, we were interested in the minimum spatial scale at which significant differences between habitats could be detected within islands. We performed multiple pairwise nonparametric Wilcoxon-Mann-Whitney tests \citep{Hollander2013} to compare dewlap coloration between sites with different habitat-types, for each pair of habitats and each variable where significant differences were detected with our analyses of variance. The P-values were adjusted using a Benjamini-Hochberg correction for multiple testing \citep{Benjamini1995}.

### 2021-05-23 ms/sections/results2.tex
addressed most immediate comments

We tested for variation in \textit{A. sagrei} dewlap coloration between populations living in three characteristic habitat-types across nine islands that span the West Indian range of the brown anole (beach scrub, primary coppice and mangroves). We found that most of the variation in coloration was partitioned between islands (two-way PERMANOVA, $F(df = 8) = 43.7$, $P = 0.0001$, explained variance $R^2 = 40.9$\%). Nonetheless, we did find evidence for differences in dewlap coloration between habitat-types, and those were mostly island-specific (habitat-by-island interaction term, $F(16) = 3.53$, $P = 0.0001$, $R^2 = 6.6$\%), with a significant portion of the variation explained by an habitat effect across all islands, but this effect was very small ($F(2) = 4.7$, $P = 0.0001$, $R^2 = 1.1$\%).\\

We subsequently tested for differences in dewlap coloration between habitat-populations within each island, using within-island principal component scores, that is, from components computed from the data specific to each island (to maximize the variation captured for each island, see Methods). Our within-island random forest classification analyses revealed detectable differences in dewlap coloration on seven out of the nine islands in our sample: Abaco, Bimini, Cayman Brac, Eleuthera, Little Cayman, Long Island, North Andros and South Andros. On these islands, our classifiers could reassign individual dewlaps to their correct habitat more often than expected by chance (Table \ref{tab:randomforests}). We obtained similar results using other machine learning approaches such as support vector machines (Table \ref{tab:ksvms}) and linear discriminant analysis (Table \ref{tab:ldas}), except that these methods did not detect significant differences on Eleuthera and North Andros. We did not find evidence of spatial autocorrelation in dewlap coloration between the sites within islands, except for Eleuthera (Table \ref{tab:autocorrelation}). We now describe the specific differences detected on each island.\\

@@

Little Cayman was characterized by a better discrimination of mangrove lizards from the rest than between beach scrub and coppice lizards (Fig. \ref{fig:LittleCayman}A). Mangrove dewlaps were possibly most distinct with respect to their reflectance in short wavelengths (Fig. \ref{fig:LittleCayman}B), with significantly lower UV reflectance (as represented by PC2, Fig. \ref{fig:LittleCayman}D, E, Table \ref{tab:anova}). Beach scrub lizards were characterized by brighter dewlaps than coppice lizards (PC1), and also more convex curves, i.e. slightly higher UV and red reflectance (as represented by higher PC3 scores), than lizards from the other two habitats (Fig. \ref{fig:LittleCayman}D, E, Table \ref{tab:anova}).\\

@@

On South Andros beach scrub and coppice dewlaps could be discriminated better against each other than with mangrove dewlaps (Fig. \ref{fig:SouthAndros}A), with importance profiles supported UV-reflectance as a predictor of coppice lizards (Fig. \ref{fig:SouthAndros}B). Coppice lizards had more curved reflectance profiles than beach scrub lizards (PC3), and lizards from both habitats differed along PC4, which is again more difficult to interpret (Fig. \ref{fig:SouthAndros}D, E, Table \ref{tab:anova}). Beach scrub lizards also differed from mangrove lizards in PC4 (Fig. \ref{fig:SouthAndros}D, E, Table \ref{tab:anova}).\\

>>>>

We tested for variation in \textit{A. sagrei} dewlap coloration between populations living in three characteristic habitat-types across nine islands that span the West Indian range of the brown anole (beach scrub, primary coppice and mangroves). We found that most of the variation in coloration was partitioned between islands (two-way PERMANOVA, $F(df = 8) = 43.7$, $P = 0.0001$, explained variance $R^2 = 40.9$\%). Nonetheless, we did find evidence for differences in dewlap coloration between habitat-types, and those were mostly island-specific (habitat-by-island interaction term, $F(16) = 3.53$, $P = 0.0001$, $R^2 = 6.6$\%), with a significant portion of the variation explained by an habitat effect across all islands, but this effect was relatively small ($F(2) = 4.7$, $P = 0.0001$, $R^2 = 1.1$\%).\\

We subsequently tested for differences in dewlap coloration between habitat-populations within each island, using within-island principal component scores (to maximize the variation captured for each island, see Methods). Our within-island random forest classification analyses revealed detectable differences in dewlap coloration on eight out of the nine islands in our sample: Abaco, Bimini, Cayman Brac, Eleuthera, Little Cayman, Long Island, North Andros and South Andros. The accuracy of Random forest classification exceeded random expectation more often than expected by chance for all these islands (Table \ref{tab:randomforests}). Accuracy was as high as 73\% for Cayman Brac. We obtained similar results using other machine learning approaches such as support vector machines (Table \ref{tab:ksvms}) and linear discriminant analysis (Table \ref{tab:ldas}), except that these methods did not detect significant differences on Eleuthera and North Andros. We did not find evidence of spatial autocorrelation in dewlap coloration between the sites within islands, except for Eleuthera (Table \ref{tab:autocorrelation}). We now describe the specific differences detected on each island.\\

The accuracy of Random forest classification exceeded random expectation more often than expected by chance for all islands. Accuracy was as high as 73% for Cayman Brac.

@@

Little Cayman was characterized by a better discrimination of mangrove lizards from the rest than between beach scrub and coppice lizards (Fig. \ref{fig:LittleCayman}A). Mangrove dewlaps were most distinct with respect to their reflectance in short wavelengths (Fig. \ref{fig:LittleCayman}B), with significantly lower UV reflectance (as represented by PC2, Fig. \ref{fig:LittleCayman}D, E, Table \ref{tab:anova}). Beach scrub lizards were characterized by brighter dewlaps than coppice lizards (PC1), and also more convex curves, i.e. slightly higher UV and red reflectance (as represented by higher PC3 scores), than lizards from the other two habitats (Fig. \ref{fig:LittleCayman}D, E, Table \ref{tab:anova}).\\

@@

On South Andros beach scrub and coppice dewlaps could be discriminated better against each other than with mangrove dewlaps (Fig. \ref{fig:SouthAndros}A), with importance profiles supporting UV-reflectance as a predictor of coppice lizards (Fig. \ref{fig:SouthAndros}B). Coppice lizards had more curved reflectance profiles than beach scrub lizards (PC3), and lizards from both habitats differed along PC4, which is again more difficult to interpret (Fig. \ref{fig:SouthAndros}D, E, Table \ref{tab:anova}). Beach scrub lizards also differed from mangrove lizards in PC4 (Fig. \ref{fig:SouthAndros}D, E, Table \ref{tab:anova}).\\
